Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-23 WSSSPE3/report/wg_appendix_best_practices.tex
Appendix D: Added in affiliations except for two.

\begin{itemize}
\item Abani Patra, University at Buffalo
\item Sandra Gesing, University of Notre Dame
\item Neil Chue Hong, Software Sustainability Institute
\item Gregory Tucker, University of Colorado at Boulder
\item Birgit Penzens, California State University Long Beach
\item Abigail Cabunoc Mayes, Mozilla Foundation
\item Jeff Carver, University of Alabama
\item Frank L\"{o}ffler, Louisiana State University 
\item Colin Venter,  University of Huddersfield
\item Lorraine Hwang, UC Davis - CIG
\item Sou-Cheng Choi, NORC at the University of Chicago \&  Illinois Institute of Technology
\item Suresh Marru, Indiana University
\item Don Middleton, NCAR 
\item Daniel Katz,  U Chicago \& Argonne
\item Kyle Niemeyer, Oregon State University
\item Jeffrey Carver, University of Alabama
\item Dan Gunter, LBNL
\item Alexander Konovalov, \choinote{TBD}
\item Tom Crick,  \choinote{TBD}

>>>>

\begin{itemize}
\item Abani Patra -- University at Buffalo
\item Sandra Gesing -- University of Notre Dame
\item Neil Chue Hong -- Software Sustainability Institute
\item Gregory Tucker -- University of Colorado at Boulder
\item Birgit Penzens -- California State University Long Beach
\item Abigail Cabunoc Mayes -- Mozilla Foundation
\item Jeff Carver -- University of Alabama
\item Frank L\"{o}ffler -- Louisiana State University 
\item Colin Venter --  University of Huddersfield
\item Lorraine Hwang -- UC Davis 
\item Sou-Cheng Choi -- NORC at the University of Chicago \&  Illinois Institute of Technology
\item Suresh Marru -- Indiana University
\item Don Middleton -- NCAR 
\item Daniel Katz --  University of Chicago \& Argonne National Laboratory
\item Kyle Niemeyer -- Oregon State University
\item Jeffrey Carver -- University of Alabama
\item Dan Gunter -- LBNL
\item Alexander Konovalov -- \choinote{TBD}
\item Tom Crick --  \choinote{TBD}
